Multispecies survey for diet comp

### 2020-11-18 SurveyDietCompTest.Rmd
aggregate survey diet dat

The current function removes predators not expected on a fish trawl survey, removes prey types that are normally not counted, then adds uniform error to half the remaining diet proportions, removes a random subet of prey accounting for <0.25 diet proportion, then renormalizes. I would rather have a function that could be used on any "survey" so have already removed hardcoded predator selection. I think also the distributional assumptions need revision; a Dirichlet seems most appropriate to simulate continuous proportions.

@@

  # read in dat, long format output of load_diet_comp, or create_survey_diet, both have layers aggregated

  # load_diet_comp has no polygon information and is proportion, create_survey_diet has polygons and is consumption in tons

  # first aggregate to global diet comp in proportion

  # then apply aggregation bias

@@

>>>>

The current function removes predators not expected on a fish trawl survey, removes prey types that are normally not counted, then adds uniform error to half the remaining diet proportions, removes a random subet of prey accounting for <0.25 diet proportion, then renormalizes. I would rather have a function that could be used on any "survey" so have already removed hardcoded predator selection. I think also the distributional assumptions need revision; a Dirichlet is most appropriate to simulate continuous proportions.

@@

  # dat can be long format output of load_diet_comp, or create_survey_diet, both have layers aggregated
  # load_diet_comp output has no polygon column and atoutput is proportion, 
  # create_survey_diet output has polygon column and atoutput is consumption in tons
  # first aggregate to get global diet comp in proportion, if not already in that form

  if("polygon" %in% names(dat)){
    #sum over boxes and assume sampling occurs coastwide (the sampled boxes were already subset in create functions)
    dat2 <- aggregate(dat$atoutput,list(dat$species,dat$agecl,dat$time, dat$prey),sum)
    names(dat2) <- c("species","agecl","time","prey", "sumcons")

  # then apply id/aggregation bias--this adds prey categories that don't exist??

@@

# global proportion diet comp for comparison with survey_cons
diettest <- load_diet_comp(here("atlantisoutput", "NOBA_march_2020"), 
                           "nordic_runresults_01DietCheck.txt", fgs = fgs) %>%
  filter(atoutput>0)
